Program Transformations for miniKanren

### 2020-07-07 papers/aplas/text/intro.tex
Intro edits

In this paper, we study issues which conjunctive partial deduction faces being applied for \mk.
We also describe a novel approach to partial deduction for relational programming, \emph{conservative partial deduction}.
We implemented this approach and compared it with the existing specialization system (\ecce) on several programs and discuss why some \mk programs run slower after specialization.

>>>>

In this paper, we study issues which conjunctive partial deduction faces being applied for \mk.
We also describe a novel approach to partial deduction for relational programming, \emph{conservative partial deduction}.
We implemented this approach and compared it with the existing specialization system (\ecce) for several programs.
We report here the result of the comparison and discuss why some \mk programs run slower after specialization.
